---
title: "The metabolic pathways between components of stature and HbA1c: Protocol for an exploratory cross-sectional analysis in the UK Biobank"
shorttitle: 
author: 
    - Luke W. Johnston
    - Daniel Ibsen
    - Daniel Witte
    - Alisa Kjærgaard
date: "`r Sys.Date()`"
author: 
  - name: Luke W. Johnston
    affiliation: "1,2"
  - name: Daniel Ibsen
    affiliation: 1
  - name: Daniel Witte
    affiliation: "1,2"
  - name: Alisa Kjærgaard
    affiliation: "1,2"
affiliation:
  - id: 1
    institution: Steno Diabetes Center Aarhus, Denmark
  - id: 2
    institution: Aarhus University, Denmark
output: 
    ukbAid::protocol_document: default
    prereg::prereg_pdf: default
    md_document: default
# bibliography: "PATH"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Please also refer to a relevant reporting checklist (e.g. STROBE) when
describing the study. Find checklists
[here](https://www.equator-network.org/)*

# Study information

## Title

`r rmarkdown::metadata$title`

## Description

There is strong evidence of a relationship between adverse early life
conditions and risk for type 2 diabetes, but it isn't well-studied in
humans how this association may be mediated metabolically. For instance,
does an adverse growth condition lead to a lower metabolic capacity to
handle nutrients like lipids, translating to higher LDL, lower HDL, and
higher glucose? Does it lead to lower capacity to resolve inflammation,
leading to slightly higher CRP? And does this lower metabolic capacity
translate to a higher risk for diabetes?

Directly studying the role of early childhood conditions on diabetes
risk is extremely difficult, if not at least practically impossible
considering we need data from an adult's childhood. However, adult leg
length is a useful biomarker of early childhood conditions, as growth
conditions can influence how much the legs grow relative to the rest of
the body.

We will use the UK Biobank Cohort to study how adult leg length mediates
risk for type 2 diabetes through standard clinical metabolic variables.
`r ukbAid::uk_protocol_statement`

## Objectives and hypotheses

Our *exporatory* aim is to identify how the components of stature
influence the metabolic profile in adults and the consequent risk for
type 2 diabetes through higher HbA1c by:

-   Exploring how components of stature relate to aspects of the
    metabolic profile

# Design plan

## Study design

This is a cross-sectional analysis of a large cohort dataset.

# Sampling plan

## Data collection procedures

*describe how the exposure was assessed*

```{r}
library(tidyverse)
read_csv(here::here("data-raw/project-variables.csv")) %>% 
    select(ukb_variable_description, link) %>% 
    filter(str_detect(ukb_variable_description, "height|leg|sitting"))
```

*describe how the outcome was assessed*

*describe how the covariates were assessed*

## Sample size

*describe the participants. Describe eligibility criteria and sources of
selection of participants. At this point it may not be possible to know
your sample size*

# Variables

## Measured variables

-   **Population:** Those without diabetes and who have had their
    stature measured in the UK Biobank.

-   **Exposures:** Height, sitting height, and leg length.

-   **Comparisons:** The exposure measures are used as continuous
    variables, so comparisons will be done on a continuum of
    increasing/decreasing exposure.

-   **Outcome:** HbA1c

*list the exposure(s)*

*list the outcome(s)*

*list the covariates*

# Analysis plan

## Statistical models

*describe your statistical analysis. This is essentially your
statistical analysis plan*

*Remember to mention statistical software to be used, analysis of
baseline characteristics, adjustment for confounding, selection of
potential confounders, examined subgroups, how missing data was handled,
how loss to follow-up was addressed and sensitivity analyses*

# Other

*add the references here*

# References

